25 Years of Water Quality Change in Rhode Island Lakes and Ponds

### 2018-09-13 manuscript/manuscript.Rmd
day one of dediated writing time

Given what is known about long term trends in water quality within the broader New England region [@Oliver_2017], we were curious if those trends were also present in water quality trends in Rhode Island lakes and ponds.  Something about spatial and temporal variability of water quality

@@

@@

# Discussion

# Conclusions

>>>>

Given what is known about long term trends in water quality within the broader region of the northeastern United States [@Oliver_2017], we were curious if those trends were also present in water quality trends in Rhode Island lakes and ponds.  Something about spatial and temporal variability of water quality

@@

## Study Area and Data

## Trend Analysis

### Z-score

### Kendall's Tau

## Individual Lakes

@@

## State-wide trends in water quality

## Individual lake trends in water quality

# Discussion and conclusions
